ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-24 paper/tables.Rmd
kill me

```{r}
tab <- dt[
    ,
    .(
      value=sprintf("%1.2f ± %1.2f", mean(value), sd(value)),
      val = mean(value),
      std = sd(value)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
tab_valid <- dt_valid[
    ,
    .(
      value=sprintf("%1.2f ± %1.2f", mean(value), sd(value)),
      val = mean(value),
      std = sd(value)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
# Order:
chosen_data <- c(
  "Linearly Separable",
  "GMSC",
  "MNIST",
)
chosen_model <- c(
  "MLP",
  "JEM",
  "LeNet-5"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <-  "Results for datasets from different domains: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-main} \\newline"
file_name <- "paper/contents/table-main.tex"
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

```{r}
# Choices:
measures <- c(
  "distance_from_energy_l2",
  "distance_from_targets_l2"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
chosen_source <- "tabular"
# Order:
chosen_data <- c(
  "GMSC",
  "California Housing",
  "German Credit"
)
chosen_model <- "MLP"

@@

>>>>

```{r}
generators <- unique(dt$generator)[sapply(unique(dt$generator), function(x) {!grepl("L1",x)})]
tab <- dt[
    generator %in% generators,
    .(
      value=sprintf("%1.2f ± %1.2f", mean(value), sd(value)),
      val = mean(value),
      std = sd(value)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
tab_full <- dt[
    ,
    .(
      value=sprintf("%1.2f ± %1.2f", mean(value), sd(value)),
      val = mean(value),
      std = sd(value)
    ),
    .(dataname, generator, model, variable, source)
]

```{r}
generators <- unique(dt$generator)[sapply(unique(dt$generator), function(x) {!grepl("L1",x)})]
tab_valid <- dt_valid[
    generator %in% generators,
    .(
      value=sprintf("%1.2f ± %1.2f", mean(value), sd(value)),
      val = mean(value),
      std = sd(value)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
# Order:
chosen_data <- c(
  "Linearly Separable",
  "GMSC",
  "MNIST"
)
chosen_model <- c(
  "MLP",
  "JEM",
  "LeNet-5"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i[,variable:=factor(variable, levels=measures)]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,model:=factor(model,levels=chosen_model)]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
tab_i[is.na(tab_i)] <- ""
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <-  "Results for datasets from different domains: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-main} \\newline"
file_name <- "paper/contents/table-main.tex"
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility",
  "distance"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓",
  "Cost ↓"
)
chosen_source <- "tabular"
# Order:
chosen_data <- c(
  "GMSC",
  "California Housing"
)
chosen_model <- c(
  "MLP",
  "JEM"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i[,variable:=factor(variable, levels=measures)]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,model:=factor(model,levels=chosen_model)]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
chosen_source <- "vision"
# Order:
chosen_data <- c(
  "MNIST"
)
chosen_model <- c(
  "MLP",
  "LeNet-5"
)

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i[,variable:=factor(variable, levels=measures)]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,model:=factor(model,levels=chosen_model)]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s dataset: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```
